Addition and removal energies of circular quantum dots

### 2017-04-23 Manuscript/paper.tex
Add extrapolation fit

>>>>

\begin{figure}
  \centering
  \includegraphics{fig-fit-2-1p0-add}
  \caption{A five-point fit of the addition energies of the $(N, \omega) = (6, 1.0)$ system.  The grey shaded region contains the masked data points, which are ignored by the fitting procedure.  The left figure plots the central difference of the addition energies $\varepsilon^{(+)}$ with respect to the number of shells $K$.  On such a plot, the power law model should appear as a straight line.  The fits are optimized using the procedure described in Section \ref{subsec:extrapolation}.  Note that the lines do not evenly pass through the points in the left plot as the fitting weights are tuned for the energy on a linear scale, not the energy differences on a logarithmic scale.}
  \label{fig:by-fit-2-1p0-add}
\end{figure}
